\section{Selling Points}\label{sec:selling_points}

Our implementation successfully utilizes blockchain technology for managing vital application data. Although this causes some non-trivial challenges, which need to be dealt with, it also provides many benefits to the users of our application. We will now take a look at some of the benefits of blockchains in the context of our application.
\begin{itemize}
  \item \textbf{Trust}: The decentralized nature of blockchains eliminates the necessity for third parties to validate transactions between interacting users. Users of our trading platform are able to interact with one another, sell and buy cars without the need of anyone to confirm or issue their transactions.
  \item \textbf{Transparency}: The Ethereum ledger is public and can be accessed by anyone. In our application we use the blockchain to manage information regarding car sales as well as sensitive car properties such as mileage. Due to the transparency of the blockchain, all users of our platform have access to this information and are able to make well-informed decisions on whether or not to buy a car.
  \item \textbf{Immutability}: Data stored in the blockchain cannot be altered retrospectively. This means that users can rest assured that vital information provided by the blockchain, such as mileage, has not been tempered with.
  \item \textbf{Availability}: Peer-to-peer blockchains consisting of numerous nodes do not have a single point of failure that may cause data loss or inability to operate. For this reason, the blockchain component of our application is fully operational at all times and is able to ensure that data provided or already present will continue to be available in the future.
  \item \textbf{Utilization}: A public blockchain may be used by many different applications. It is imaginable that the blockchain component of our application could also be used by other applications, such as other trading platforms. This may increase the number of platform providers from which customers can choose in the future, while retaining the same benefits.
  \item \textbf{Performance}: Although the transaction performance of blockchains is a critical topic, many promising efforts are already made to increase their performance significantly. This would potentially enable users of our application to issue transactions at a much higher pace than they could with traditional methods.
  \item \textbf{Lower Fees}: Unlike other trading platforms where you may have to pay a fee to use their services, our application only requires you to pay the price it costs to put your content onto the blockchain.
\end{itemize}
All in all, our application leverages many of the benefits that blockchains already provide and will further benefit from any future development in that area.
